|

### 2021-05-31 article/article.Rmd
small changes in article

Since many empirical tests of the "law of $1/n$" have produced conflicting
results, scholars have expanded this research agenda and closely investigated
how institutional factors condition the original formulation of the theory. For
instance, authors such as @crowley2019law and @pecorino2018supermajority
accurately point out that collective action problems have been overlooked in
the literature, and recent findings indicate that bicameralism
[@maldonado2013legislatures], intergovernmental competition
[@crowley2015local], redistricting [@lee2018court], and party ideology
[@bjedov2014impact] strongly influence the relationship between seats and
spending. Moreover, the literature has increasingly applied causal inference
designs to estimate the effect of the "law of $1/n$", and in contrast to
previous studies using panel data, regression discontinuity designs generally
indicate that more legislators decrease public expenditures
[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
respect, scholars have long been aware of the theoretical and empirical
limitations of the "law of $1/n$", and the proliferation of new studies reflect
a conscious attempt to assess the robustness of the theory [@crowley2019law].

@@

We run binomial tests and meta-regressions to further evaluate the relationship
between legislature size and government expenditures. We use binomial tests
to assess whether the proportions of positive and negative coefficients in our
sample are statistically different from each other. In the meta-regressions, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. As our sample includes both published and
unpublished articles, we also construct a series of funnel plots to test for
publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

Aggregate results indicate that legislature size has no significant impact on
public spending. All of our main meta-analysis estimates show that the overall
effect is not statistically different from zero, thus confirming the
conflicting findings reported by the literature. However, when we look only at
articles that employ regression discontinuity designs, we see that all three
papers included in our sample suggest that a higher number of legislators leads
to lower public spending [@debenedetto2018effect; @hohmann2017effect;
@lewis2019legislature]. In this regard, it is possible that methodological
choices partially explain the divergent results observed in the literature, as
studies that use causal inference methods consistently point to the same
direction. One limitation of this finding is that these studies only test the
impact of lower house size on the natural logarithm of expenditure per capita,
thus it remains unclear whether the results hold with other variables.

The meta-regressions provide additional evidence that our study sample is
highly heterogeneous and that effect sizes differ substantially according to
study specifications. When using our extended sample of `r dim(fulldat)[1]`
coefficients, we find that unicameralism is associated with higher public
spending, as predicted by the "law of $1/n$". Since most unicameral
legislatures are located in local governments (municipalities or districts),
this result supports the theory strictly in its first formulation. Moreover,
our meta-regressions indicate that larger upper chambers spend more in terms of
per capita expenditure than lower chambers, a result that also appears in the
binomial tests. Non-majoritarian voting systems decrease government spending as
a percentage of GDP, but they do not have a relevant impact on the other
measures of public expenditure, following the idea that the $1/n$ effect grows
weaker as the empirical cases distance from the original definition of the law.
Finally, meta-regression results confirm that regression discontinuity models
reduce public spending estimates.

In summary, our results are in line with previous findings that lend partial
support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
An assessment of the effects of collective action costs in these analyses is
crucial to determine the full mechanism operating behind these results.
Overall, our analysis does not provide robust support for the theory as
originally conceived.

@@

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that were published in English and
cited \citet{weingast1981political}, as it is the foundational work in the
literature on the "law of $1/n$". To ensure that our sample was comparable, we
only selected papers that used quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study sample
uses (i) public expenditure as a share of GDP; (ii) public expenditure per
capita; and (iii) the natural logarithm of public expenditure per capita as its
main variables of interest. In regards to legislature size, the variables are
(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
upper house size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. This search
added two new results to our sample [@coate2011government;
@debenedetto2018effect], but neither of them included variables beyond the six
measures we had previously identified. In the third search round, we looked
into the personal webpages of every author whom we had already included in our
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript that we had missed in the two former
queries. All papers we found in the last search had already been included in
our sample. The full list of excluded records is available for online
consultation in the replication materials. Combined, the three searches
produced a dataset of `r length(unique(dat$id))` studies as of the
10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
list of articles we analyse in this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign2, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign2[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ$=$National Tax Journal.}
\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference
designs such as instrumental variables and regression discontinuity models to
test the relationship between house size and public spending.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original definition of the "law of $1/n$"
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`). 
These six variables formed a $3 \times 3$ table, yet not all combinations were
available in the data. We found no studies that correlate public expenditure
per capita with either upper chamber size or the natural logarithm of lower
house size. Thus, our meta-analysis contains seven of the nine possible
variable combinations.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign2) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign2,
         `Electoral system`      = elecsys2)

@@

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets in their models,
and almost all papers fit more than one regression with similar variables, what
suggests that the assumption above does not hold. We use two procedures to tackle this
problem. First, we created two sets of study coefficients to reduce the impact
of multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
articles analysed two dependent or independent variables of
interest\footnote{The papers that used more than one dependent or independent
variable of interest are \citet{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are very similar when we use the extended
set.

@@

The "law of $1/n$" states that more legislators increase government
expenditure. In this paper, we employ three methods to test the empirical
validity of that relationship. First, we run binomial z-tests to assess the
frequency of positive and negative coefficients in our sample. Then, we fit 9
multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
Lastly, we run two sets of meta-regressions to measure the effects of a group
of moderators on the effect sizes of our study sample. To recapitulate, our
independent variables of interest are lower chamber size, the natural logarithm
of lower chamber size, and upper chamber size. The dependent variables are
public expenditure per capita, the natural logarithm of public expenditure per
capita, and government expenditure as a percentage of GDP. Since the outcomes
have different scales, we treat them separately in our models.

@@

The binomial z-test evaluates whether the majority of the coefficients of our
independent variables are positive or negative[^binomial]. If increasing the
number of legislators leads to higher public expending, we should expect most
coefficients to be positive. Conversely, if the "reverse law of $1/n" is true,
our results should indicate that $p < 0.5$, that is, the proportion of positive
coefficients is lower than 0.5. The null hypothesis here states that the sign
of the coefficient is equally likely to be positive or negative.

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in the
article pool. Our sample does not contain any papers that analyse the
relationships between the log lower chamber size and public expenditure per
capita, or between upper chamber size and the logarithm of public expenditure
per capita. We calculated the effect sizes by drawing the coefficients and
standard errors from the articles and computing Hedges' $g$, which is a widely
used measure of standardised difference between means. When standard errors
were not directly available in the texts, we used t-statistics to retrieve
them.

@@

@@

\caption{Meta Regression Results\label{tabregressions}}
\footnotesize

@@

\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{Full Model} \\

@@

Independent Variable: log($N$) & 

@@

Independent Variable: $N$ &

@@

Non-Majoritarian (PR \& Mixed) & 

>>>>

Since many empirical tests of the "law of $1/n$" have produced conflicting
results, scholars have expanded this research agenda and closely investigated
how institutional factors condition the original formulation of the theory. For
instance, authors such as @crowley2019law and @pecorino2018supermajority
accurately point out that collective action problems have been overlooked in
the literature, and recent findings indicate that bicameralism
[@maldonado2013legislatures], intergovernmental competition
[@crowley2015local], redistricting [@lee2018court], and party ideology
[@bjedov2014impact] strongly influence the relationship between seats and
spending. Moreover, the literature has increasingly applied causal inference
methods to estimate the effect of the "law of $1/n$", and in contrast to
previous studies using panel data, regression discontinuity designs generally
indicate that more legislators decrease public expenditures
[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature;
@petterssonlidbom2012size]. In this respect, scholars have long been aware of
the theoretical and empirical limitations of the "law of $1/n$", and the
proliferation of new studies reflect a conscious attempt to assess the
robustness of the theory.

@@

We run binomial tests and meta-regressions to further evaluate the relationship
between legislature size and government expenditures. We use binomial tests to
assess whether the proportions of positive and negative coefficients in our
sample are statistically different from each other. In the meta-regressions, we
measure the effect of five moderators that capture different sources of
heterogeneity in the literature. We also construct a series of funnel plots to
test for publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

Aggregate results indicate that legislature size has no significant impact on
public spending. All of our main meta-analysis estimates show that the overall
effect is not statistically different from zero, thus confirming the
conflicting findings reported by the literature. However, when we look only at
articles that employ regression discontinuity designs (RDDs), we see that all
four papers included in our sample suggest that a higher number of legislators
leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size]. In this regard, it is
possible that methodological choices partially explain the divergent results
observed in the literature, as articles that use RDDs consistently point to the
same direction. One limitation of this finding is that these studies only test
the impact of lower house size on the natural logarithm of expenditure per
capita, thus it remains unclear whether the results hold with other variables.

The meta-regressions provide additional evidence that our study sample is
highly heterogeneous and that effect sizes differ substantially according to
study specifications. When using an extended sample of `r dim(fulldat)[1]`
coefficients, we find that unicameralism is associated with higher public
spending, as predicted by the "law of $1/n$". Since most unicameral
legislatures in our sample are local governments (municipalities or districts),
this result supports the predictions of @weingast1981political. Moreover,
our meta-regressions indicate that larger upper chambers spend more in terms of
per capita expenditure than lower chambers, a result that also appears in the
binomial tests. Non-majoritarian voting systems decrease government spending as
a percentage of GDP, but they do not have a relevant impact on the other
measures of public expenditure, following the idea that the $1/n$ effect grows
weaker as the empirical cases distance from the original definition of the law.
Finally, meta-regression results confirm that regression discontinuity designs
reduce public spending estimates.

@@

We compiled our study sample in three search rounds. In the first round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that were written in English and
cited \citet{weingast1981political}, as it is the foundational work in the
literature on the "law of $1/n$". To ensure that our sample was comparable, we
only selected papers that used quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study sample
uses (i) public expenditure as a share of GDP; (ii) public expenditure per
capita; and (iii) the natural logarithm of public expenditure per capita as its
main variables of interest. In regards to legislature size, the variables are
(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
upper chamber size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. The search string contained terms strongly associated with the
literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
"lower chamber size" OR "council size" OR "parliament size" OR "legislature
size" OR "number of legislators" OR "legislative size") AND ("spending" OR
"expenditure" OR "government size")`. We again restricted the search to
articles written in English which employed quantitative methods. This search
added two new results to our sample [@coate2011government;
@debenedetto2018effect], but neither of them included variables beyond the six
measures we had previously identified. In the third search round, we looked
into the personal webpages of every author whom we had already included in our
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript that we had missed in the two former
queries. We did not find any new article that satisfied the inclusion criteria
in this search. The full list of excluded records is available for online
consultation in the replication materials. Combined, the three searches
produced a dataset of `r length(unique(dat$id))` studies as of the
10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
list of articles we analyse in this paper.

\scriptsize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\scriptsize
\footnotetext{\scriptsize \textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ $=$ National Tax Journal.}
\footnotetext{\scriptsize \textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\scriptsize \textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\scriptsize \textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\scriptsize \textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference
models such as instrumental variables and regression discontinuity designs to
test the relationship between house size and public spending.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original definition of the "law of $1/n$"
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`). 
These variables formed a $3 \times 3$ table, yet not all combinations were
available in the data. We found no studies that correlate public expenditure
per capita with either upper chamber size or the natural logarithm of lower
house size. Thus, our meta-analysis contains seven of the nine possible
variable combinations.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)
aux$`Independent Variables` <- recode(aux$`Independent Variables`,
                                      `N` = "Lower Chamber Size",
                                      `K` = "Upper Chamber Size",
                                      `logN` = "Log of Lower Chamber Size")
aux$`Electoral system` <- recode(aux$`Electoral system`,
                                 `Non-Maj` = "Non-Majoritarian",
                                 `Maj` = "Majoritarian")
aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)

@@

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use the same datasets, and almost all papers fit more
than one regression with similar variables, what suggests that the assumption
above does not hold. We use two procedures to tackle this problem. First, we
created two sets of study coefficients to reduce the impact of
multicollinearity in our estimations. The first group includes only the most
rigorous models from each paper, that is, those estimated with the largest $n$,
most control variables, and fixed effects if the authors added them. If the
article employed a regression discontinuity design, we chose the coefficient
from the optimal bandwidth or from the intermediate one. This sample
encompasses `r dim(dat)[1]` estimates, as 
`r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest\footnote{The papers that used more than one
dependent or independent variable of interest are \citet{baqir1999districts,
bjedov2014impact, bradbury2001legislative, chen2007law, crowley2019law,
erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
papers. Here we focus on the results for our restricted sample as we consider
them more robust, but the findings are nearly identical when we use the extended
set.

@@

The "law of $1/n$" states that more legislators increase government
expenditure. In this paper, we employ three methods to test the empirical
validity of that relationship. First, we run binomial z-tests to assess the
frequency of positive and negative coefficients in our sample. Then, we fit
nine multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
Lastly, we run four sets of meta-regressions to measure the effects of a group
of moderators on the effect sizes of our study sample. To recapitulate, our
independent variables of interest are lower chamber size, the natural logarithm
of lower chamber size, and upper chamber size. The dependent variables are
public expenditure per capita, the natural logarithm of public expenditure per
capita, and government expenditure as a percentage of GDP. Since the outcomes
have different scales, we treat them separately in our models.

@@

The binomial z-test evaluates whether the majority of the coefficients of our
independent variables are positive or negative[^binomial]. If increasing the
number of legislators leads to higher public expending, we should expect most
coefficients to be positive. Conversely, if the "reverse law of $1/n$" is true,
our results should indicate that $p < 0.5$, that is, the proportion of positive
coefficients is lower than 0.5. The null hypothesis here states that the sign
of the coefficient is equally likely to be positive or negative.

@@

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the nine variable combinations, we found only seven the article
pool. Our sample does not contain any papers that analyse the relationships
between log lower chamber size and public expenditure per capita, or between
upper chamber size and the logarithm of public expenditure per capita.

@@

The uppermost row shows the results for lower chamber size in our restricted
sample. In the first model, which correlates lower house and expenditure per
capita, we find a standardised mean difference (SMD) of 0.022 and a standard
error of 0.131 (figure 1.1, studies = `r mod[[1]]$k`, 95\% CI = [-0.256;
0.299], $p$-value = 0.87), so we cannot rule out that the effect is 
zero. Indeed, the effect of lower chamber size on the other two dependent
variables is also null in statistical terms. When we compare lower chamber size
with log expenditure per capita, the overall effect size is -0.031 and the
standard error is 0.049 (figure 1.2, studies = `r mod[[3]]$k`, 95\% CI =
[-0.188; 0.127], $p$-value = 0.58). The impact of larger lower houses on
government spending as a percentage of GDP  is also negligible (figure 1.3,
studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI = [-0.0334; 0.021], $p$-value
= 0.563). The results are virtually identical when we estimate the
meta-analyses using our extended sample, and all three coefficients are
again statistically indistinguishable from zero.

@@

\caption{Meta-regression results\label{tab:regressions}}
\scriptsize

@@

\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{All Coefficients} \\

@@

Log of Lower Chamber Size & 

@@

Lower Chamber Size &

@@

Non-Majoritarian & 
